%====================
% PERSONAL INFO
%====================
\newcommand{\FullName}{Rahat Sayyed}

% HEADER ITEMS {DISPLAY_TEXT}{LINK or empty}
\DeclareHeaderItem{Loc}{Pune, India}{}
\DeclareHeaderItem{Email}{rahxtsayyed@gmail.com}{mailto:rahxtsayyed@gmail.com}
\DeclareHeaderItem{Site}{rahatsayyed.xyz}{https://rahatsayyed.xyz}
\DeclareHeaderItem{GitHub}{github.com/rahatsayyed}{https://github.com/rahatsayyed}
\DeclareHeaderItem{LinkedIn}{in/rahatsayyed}{https://linkedin.com/in/rahatsayyed}


%====================
% SUMMARY
%====================
\newcommand{\SummaryText}{
Full-stack and Blockchain Developer with 3+ years of experience building Web3 platforms and production-grade smart contracts.
Delivered systems handling 200+ secure transactions with zero disputes, optimized contracts to reduce fees by 35\%, and maintained 99.9\% uptime.
Strong focus on Cardano ecosystem, frontend engineering, and secure distributed systems.
}

%====================
% SKILLS
%====================
\newcommand{\Skills}{JavaScript, TypeScript, Aiken, Solidity, Cardano CLI, Lucid.js, Mesh.js, Blockchain Security, React.js, Next.js, TailwindCSS, Node.js, Express.js, REST APIs, MongoDB, Firestore}

\newcommand{\JobTitle}{Full-stack and Blockchain Developer}

%====================
% EXPERIENCE
%====================
% ---- Job definitions ----
% \job{ROLE}{COMPANY}{LINK}{DATES}{BULLETS}
\DeclareJob{JobOne}{
  \job
    {Web 3.0 Developer}
    {Konma Dao}
    {https://www.konma.io}
    {2023 -- Present}
    {
      \item Built Next.js-based frontend integrated with Lucid.js for multichain DEX aggregation, improving swap success rate to 95\%.
      \item Developed secure Aiken smart contracts for carbon credit marketplace, achieving 99.9\% uptime and eliminating double-spend vulnerabilities.
      \item Reduced transaction fees by 35\% by refactoring on-chain architecture and optimizing contract execution paths.
      \item Delivered blockchain registry supporting 300+ verified offset projects using Cardano integrations.
      \item Created 5+ reusable React components, reducing feature delivery time by 40\%.
    }
}

\DeclareJob{JobTwo}{
  \job
    {Independent \& Academic Projects}
    {}
    {}
    {}
    {
      \item Built Talendro, a decentralized freelance platform with escrow smart contracts supporting 200+ dispute-free transactions.
      \item Developed reputation-based staking mechanism improving trust across 70+ freelancers and clients.
      \item Contributed to AI-driven hiring platform (HirEx) reducing time-to-hire by 60\%.
    }
}



%====================
% EDUCATION
%====================
% \DeclareEducation{EduName}{\education{Degree}{University}{Dates}{BulletPoint}}
\DeclareEducation{EduOne}{
  \education
    {Bachelors’ of Engineering: Computer Engineering}
    {Keystone School of Engineering, Pune}
    {2023}
    {}
}

%====================
% CERTIFICATIONS
%====================
% \DeclareCertification{CertName}{\certification{CertName}{IssuingOrganization(Year)}{BulletPoint}}
\DeclareCertification{CertAiken}{
  \certification
    {Certified Aiken Developer}
    {Emurgo Academy (2024)}
    {}
}

\DeclareCertification{CertCardano}{
  \certification
    {Cardano Blockchain Certified Associate}
    {Cardano Foundation (2023)}
    {}
}

\DeclareCertification{CertEth}{
  \certification
    {Ethereum and Solidity Intensive Program}
    {Codedamn}
    {}
}

\DeclareCertification{CertHaskell}{
  \certification
    {Haskell \& Plutus Training}
    {Konma}
    {}
}
